Actuator line modeling of vertical-axis turbines

### 2016-05-02 paper.tex
Remove comment about free-wake vortex method computational cost

The ALM provides a more physical flow description compared to momentum and
potential flow vortex models, at a reasonable cost. The ALM has an important
advantage over vortex methods in that the effort solving the flow field remains
reasonably constant as a simulation progresses, whereas free-wake vortex methods
typically increase in computational complexity each time step. This is
especially important for array simulations, where for a given domain adding many
turbines will be cheap in the ALM compared to the rapidly increasing number of
vortex elements generated by each turbine. The ALM also drastically reduces
computational effort compared to blade-resolved CFD, while maintaining the
unsteadiness of the wake not resolved by a conventional actuator disk.
Furthermore, its implementation within finite volume CFD provides a convenient
way to study turbine array siting, since effects like terrain and buildings can
be included, as can no-slip boundary conditions and boundary layer inflow
profiles. Since the turbinesFoam library developed here uses OpenFOAM's modular
\texttt{fvOptions} framework, the ALM body force term can be added as-is to
compressible or multiphase solvers, for exploring more complicated physics.
These features would be difficult or impossible to implement in a momentum or
vortex models.

>>>>

The ALM provides a more physical flow description compared to momentum and
potential flow vortex models, at a reasonable cost. The ALM also drastically
reduces computational effort compared to blade-resolved CFD, while maintaining
the unsteadiness of the wake not resolved by a conventional actuator disk.
Furthermore, its implementation within finite volume CFD provides a convenient
way to study turbine array siting, since effects like terrain and buildings can
be included, as can no-slip boundary conditions and boundary layer inflow
profiles. Since the turbinesFoam library developed here uses OpenFOAM's modular
\texttt{fvOptions} framework, the ALM body force term can be added as-is to
compressible or multiphase solvers, for exploring more complicated physics.
These features would be difficult or impossible to implement in a momentum or
vortex models.
